---
title: "quiz1"
author: "Tianming"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1.The en_US.blogs.txt | en_US.blogs.txt   file is how many megabytes?
```{r}
fileinfor <- file.info("./final/en_US/en_US.blogs.txt")
fileinfor$size/1024.0^2
```


Q2.The en_US.twitter.txt has how many lines of text?
```{r}
enUStwitter <- "./final/en_US/en_US.twitter.txt"
enUStwitter <- readLines(enUStwitter, skipNul = TRUE)
length(enUStwitter)
```


Q3. What is the length of the longest line seen in any of the three en_US data sets?
```{r}
enUSnews <- "./final/en_US/en_US.news.txt"
enUSnews <- readLines(enUSnews, skipNul = TRUE)
enUSblogs <- "./final/en_US/en_US.blogs.txt"
enUSblogs <- readLines(enUSblogs, skipNul = TRUE)

max(nchar(enUStwitter))
max(nchar(enUSblogs))
max(nchar(enUSnews))
```


Q4. In the en_US twitter data set, if you divide the number of lines where the<br\>
"love" (all lowercase) occurs by the number of lines the word "hate" (all lowercase)<br\>
occurs, about what do you get?
```{r}
UStwitter.love <- grepl(".love.", enUStwitter)
length(enUStwitter[UStwitter.love])

UStwitter.hate <- grepl(".hate.", enUStwitter)
length(enUStwitter[UStwitter.love])/length(enUStwitter[UStwitter.hate])
```


Q5. The one tweet in the en_US twitter data set that matches the word "biostats" says that?
```{r}
 enUStwitter[grepl("biostats", enUStwitter)]
```


Q6. How many tweets have the exact characters "A computer once beat me at chess, but it was <br\> no match for me at kickboxing". (i.e. the line matches those characters exactly.)
```{r}
table(grepl( "A computer once beat me at chess, but it was no match for me at kickboxing", enUStwitter))
```





















